In-silico molecular enrichment and clearance of the human intracranial space

### 2024-11-27 paper/main.tex
Fix simple addition ;-)
Former-commit-id: 040a8657f636cd392eb5e965529b88b89ed5f0a3 [formerly 0c67e9ac2b4024d14c6260c7dd13c93919b42c76]
Former-commit-id: 89abed48071cb04d72d2068e47f53a6d0e9e6269
Updates from Overleaf

\mer{MER: Target length: 5000 words (Intro, Results, Discussion) plus <3000 words Methods: 800 words Introduction. 2800 words Results. 1800 words Discussion.}

@@

\subsection*{The significance of perivascular spaces as flow highways}
\begin{itemize}
\item
  Perivascular flow and transport has been identified as a key
  mechanism and potential target for enhancing brain drug delivery and
  metabolic waste clearance -- what are the global (intracranial)
  effects of such intracranial highways? 
\item
  Do solutes move from PVS to the SAS, or both along the PVS and along
  the SAS?
\end{itemize}
\begin{figure}
    \centering
    \includegraphics[height=\textheight]{figures/figure3.png}
    \caption{\mer{MER: Put vasculature network illustration here. Many aspects actually. Marking of segments. Location relative to 3D. Radius etc. Marius will evaluate and suggest. Results: Group segments by logical order. For key arterial segments: average radius and length (can be moved to Supplementary if need be); pressure values; flow velocities; and then histograph with flow velocities for each mesh cell. Make sure to minorly note that ACA refers to a segment of the ACA and not the whole thing e.g.}}
    \label{fig:pvs}
\end{figure}
\Cref{fig:pvs}.

@@

From T1-weighted MR images of a human subject~\cite{hodneland2019new},
we first automatically segment the brain parenchyma and CSF spaces,
including the ventricular system and SAS, using
Synthseg~\cite{billot2023robust,billot2023synthseg}. We next manually
adjust the segmentation to accurately represent the connections
between CSF spaces (aqueduct, median aperture), smoothen, and finally
extract surface representations of the outer (arachnoid) boundary, the
pial membrane and other interfaces. Conforming to these surface and
interface representations, we generate a tetrahedral mesh $\Omega$
representing the complete intracranial volume as the union of the
parenchyma $\Omega_{\rm PAR}$ and CSF spaces $\Omega_{\rm CSF}$, using
fTetWild~\cite{hu2020fast}. The resulting computational mesh consists
of $153\,729$ vertices and $851\,904$ mesh cells, which vary between
$0.4$ mm and $1.2$ cm in mesh cell diameter. The parenchyma has a
total volume of $1386$ ml, whereas the ventricles and the outer SAS
contribute $28$ ml and $277$ ml, respectively, to a total CSF volume
of $305$ml, in agreement with recent
estimates~\cite{hladky2024regulation}.

>>>>

\mer{MER: Target length: 5000 words (Intro, Results, Discussion) plus <3000 words Methods: 700 words Introduction. 2800 words Results. 1500 words Discussion.}

@@

\subsection*{The significance of perivascular spaces as flow highways}
\begin{itemize}
\item
  Perivascular flow and transport has been identified as a key
  mechanism and potential target for enhancing brain drug delivery and
  metabolic waste clearance -- what are the global (intracranial)
  effects of such intracranial highways? 
\item
  Do solutes move from PVS to the SAS, or both along the PVS and along
  the SAS?
\end{itemize}

\paragraph{PVS Flow velocities}
\begin{itemize}
    \item we consider three different PVS flow fields: PVS flow driven by production field pressure differences, cardiac peristaltic flow and vasomotion peristaltic flow. 
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[height=\textheight]{figures/figure3.png}
    \caption{\mer{MER: Put vasculature network illustration here. Many aspects actually. Marking of segments. Location relative to 3D. Radius etc. Marius will evaluate and suggest. Results: Group segments by logical order. For key arterial segments: average radius and length (can be moved to Supplementary if need be); pressure values; flow velocities; and then histograph with flow velocities for each mesh cell. Make sure to minorly note that ACA refers to a segment of the ACA and not the whole thing e.g.}}
    \label{fig:pvs}
\end{figure}
\Cref{fig:pvs}.

@@

From T1-weighted MR images of a human subject~\cite{hodneland2019new},
we first automatically segment the brain parenchyma and CSF spaces,
including the ventricular system and SAS, using
Synthseg~\cite{billot2023robust,billot2023synthseg}. We next manually
adjust the segmentation to accurately represent the connections
between CSF spaces (aqueduct, median aperture, tentorium cerebelli), smoothen, and finally
extract surface representations of the outer (arachnoid) boundary, the
pial membrane and other interfaces. Conforming to these surface and
interface representations, we generate a tetrahedral mesh $\Omega$
representing the complete intracranial volume as the union of the
parenchyma $\Omega_{\rm PAR}$ and CSF spaces $\Omega_{\rm CSF}$, using
fTetWild~\cite{hu2020fast}. The resulting computational mesh consists
of $221\,988$ vertices and $1\,225\,774$ mesh cells, which vary between
$0.24$ mm and $1.29$ cm in mesh cell diameter. The parenchyma has a
total volume of $1318$ ml, whereas the ventricles and the outer SAS
contribute $32$ ml and $328$ ml, respectively, to a total CSF volume
of $360$ml, in agreement with recent estimates~\cite{hladky2024regulation}.
